---
title: "Results Analysis"
author: "Annie Whamond"
date: "2024-04-10"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages

```{r}
# Load libraries
library(here)
library(lsr)
library(dplyr)
library(tidyverse)
library(tidylog)
library(binom)
library(assertthat)
library(kableExtra)
library(webshot2)
```

# Load data

```{r}
# Load preprocessed data
d_articles <- read_csv(here('data', 'processed', 'd_articles.csv'), show_col_types = F) # article data 
d_journals <- read_csv(here('data', 'processed', 'd_journals.csv'), show_col_types = F) # journal data
```

*Note.* PPC = post-publication critique

# STUDY ONE: JOURNAL POLICY

Remove excluded, non-empirical, journals and create separate tibbles for prominent and randomly selected journals
```{r}
dj_prominent <- d_journals %>%
  filter(sample_id != "random") %>%
  filter(is_empirical == TRUE)

dj_random <- d_journals %>%
  filter(sample_id != "prominent") %>%
  filter(is_empirical == TRUE)
```

Run assertion checks for both samples
```{r}
# Check all randomly-selected and non-empirical journals have been removed from dj_prominent
assert_that(
  all(dj_prominent$sample_id == "prominent" | dj_prominent$sample_id == "both" 
      & dj_prominent$is_empirical == TRUE),
  msg = "Found unexpected values in the sample_id or is_empirical columns"
  )

# Check all prominent sample and non-empirical journals have been removed from dj_random
assert_that(
  all(dj_random$sample_id == "random" | 
        dj_random$sample_id == "both" 
      & dj_random$is_empirical == TRUE),
  msg = "Found unexpected values in the sample_id or is_empirical columns"
  )
```

## Journal characteristics

*Descriptive statistics*

Calculate JIF median and IQR for random journals
```{r}
randomJIF <- dj_random %>% 
  filter(ppc_type == "A") %>%
  filter(!is.na(jif)) %>%
  summarise(randMedian_jif = round(median(jif),2),
            randMin_jif = round(min(jif),2),
            randMax_jif = round(max(jif),2),
            randIQR_jif = round(IQR(jif),2)
  )

randomJIF
```

Calculate JIF median and IQR for prominent journals
```{r}
# Prominent journal sample
prominentJIF <- dj_prominent %>% 
  filter(ppc_type == "A") %>%      # Keep only single entry for each journal
  summarise(promMedian_jif = round(median(jif),2), 
            promMin_jif = round(min(jif),2),
            promMax_jif = round(max(jif),2),
            promIQR_jif = round(IQR(jif),2)
  )

prominentJIF
```
Count randomly selected journals listed as COPE members 
```{r}
randomCOPE <- dj_random %>%
  filter(ppc_type == 'A') %>%
  filter(cope == TRUE) %>%
  summarise(count = n())

randomCOPE
```

Count prominent journals listed as COPE members 
```{r}
prominentCOPE <- dj_prominent %>%
  filter(ppc_type == 'A') %>%
  filter(cope == TRUE) %>%
  summarise(count = n())

prominentCOPE
```

*Supplementary Information I: Descriptive statistics for both journal samples*

Random journals Web Of Science categories
```{r}
randomCategory <- dj_random %>%
  filter(ppc_type == 'A') %>%
  group_by(field) %>%
  summarise(count = n()) %>%
  ungroup()

randomCategory
```

Prominent journals Web Of Science categories
```{r}
prominentCategory <- dj_prominent %>%
  filter(ppc_type == 'A') %>%
  group_by(field) %>%
  summarise(count = n()) %>%
  ungroup()

prominentCategory
```

## How many journals offer post-publication critique?

**RANDOMLY-SELECTED SAMPLE**

Inspect how frequently PPC policies were stated for randomly selected journals 
```{r}
randomPPC <- dj_random %>%
  filter(ppc_type == 'A') %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  ungroup()

randomPPC
```

Get the names of the randomly selected journals that have 'NO EXPLICIT' PPC options
```{r}
dj_random %>%
  filter(ppc_type == "A" & has_ppc == "NO EXPLICIT") %>%
  print()
```

Calculate confidence interval for explicitly stated PPC policies among randomly selected journals
```{r}
randomPPCyes <- dj_random %>%
  filter(ppc_type == 'A', !is.na(ppc_name)) %>%
  summarise(count = n())

randomPPCno <- dj_random %>%
  filter(ppc_type == 'A', is.na(ppc_name)) %>%
  summarise(count = n())

# Calculate Wilson confidence intervals
sample_size <- 100
confidence_level <- 0.95

# CIs for 'Yes Explicit'
randomPPC_CI <- binom.confint(randomPPCyes, sample_size, method = "wilson", conf.level = confidence_level)

# CIs for 'No' (both explicit and Implicit)
randomPPC_CI_neg <- binom.confint(randomPPCno, sample_size, method = "wilson", conf.level = confidence_level)

# View results
randomPPC_CI
randomPPC_CI_neg
```
*Note.* CIs were not calculated for the prominent sample of journals as they represented our entire population of interest.

Get names for randomly selected journals that offered more than one type of PPC
```{r}
# Return all rows with ppc_name values for ppc_type B and C
dj_random %>%
  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name))) %>%
  print()
```

Get the names of the randomly selected journals that have 'NO EXPLICIT' PPC options
```{r}
dj_random %>%
  filter(ppc_type == "A" & has_ppc == "NO EXPLICIT") %>%
  print()
```

Inspect PPC types at randomly selected journals
```{r}
table(dj_random$ppc_name)
```

Inspect the COPE status of randomly selected journals with and without PPC policies
```{r}
randomCOPE <- dj_random %>%
 filter(ppc_type == "A") %>%
 mutate(has_ppc = case_when(
    has_ppc == "NO EXPLICIT" ~ "NO",
    has_ppc == "NO IMPLICIT" ~ "NO",
    TRUE ~ has_ppc
 )) %>%
 group_by(has_ppc) %>%
 summarise(
    total_count = n(),
    COPE_count = sum(cope == TRUE)
 ) %>%
 mutate(COPEpercentage = round((COPE_count / total_count) * 100)) %>%
 ungroup()

randomCOPE
```

**PROMINENT SAMPLE**

Inspect how frequently PPC policies were stated for prominent journals 
```{r}
prominentPPC <- dj_prominent %>%
  filter(ppc_type == 'A') %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  ungroup()

prominentPPC
```

Get the names of the prominent journals that have 'NO EXPLICIT' PPC options
```{r}
dj_prominent %>%
  filter(ppc_type == "A" & has_ppc == "NO EXPLICIT") %>%
  print()
```

Get names for prominent journals that offered more than one type of PPC
```{r}
# Return count
dj_prominent %>%
  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name))) %>%
  print()
```

Inspect PPC types at prominent journals
```{r}
table(dj_prominent$ppc_name)
```

Inspect the COPE status of prominent journals with and without PPC policies
```{r}
promCOPE <- dj_prominent %>%
 filter(ppc_type == "A") %>%
 mutate(has_ppc = case_when(
    has_ppc == "NO EXPLICIT" ~ "NO",
    has_ppc == "NO IMPLICIT" ~ "NO",
    TRUE ~ has_ppc
 )) %>%
 group_by(has_ppc) %>%
 summarise(
    total_count = n(),
    COPE_count = sum(cope == TRUE)
 ) %>%
 mutate(COPEpercentage = round((COPE_count / total_count) * 100)) %>%
 ungroup()

promCOPE
```

# What limits did journals place on post-publication critique?

Find the most restrictive length limit of any journal
```{r}
# Find the lowest length limit
minLength <- d_journals %>%
 select(c(sample_id, journal_name, ppc_name, ppc_length)) %>%
 filter(!is.na(ppc_name),
         ppc_length != "NOT STATED" & ppc_length != "Qualitative") %>%
 mutate(quantLength = as.numeric(ppc_length)) %>%
 slice_min(quantLength, n = 1) %>% # Select the row with the minimum quantLength
 ungroup()

minLength
```

Find the most restrictive time limit of any journal
``` {r}
# Find the lowest time-to-submit limit
minTime <- d_journals %>%
 select(c(sample_id, journal_name, ppc_name, ppc_time)) %>%
 filter(!is.na(ppc_name),
         ppc_time != "NOT STATED" & ppc_time != "Qualitative") %>%
 mutate(quantTime = as.numeric(ppc_time)) %>%
 slice_min(quantTime, n = 1) %>% # Select the row with the minimum quantTime
 ungroup()

minTime
```

## Calculations for Table 1: PPC limits in randomly selected journals

Check length limits placed on PPC options in randomly selected journals
```{r}
# Summarise length statistics for All Types
randomLengthAll <- dj_random %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_length)) %>%
 mutate(quantLength = case_when(
    ppc_length == "NOT STATED" | ppc_length == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_length) # create a column that contains only quantitative limits
  )) %>%
 summarise(
    anyLimit = n() - sum(ppc_length == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_length == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianLength = median(quantLength, na.rm = TRUE),
    Q1 = round(quantile(quantLength, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantLength, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1)
 ) 

# Put results into desired table format
randomLengthAll_1 <- randomLengthAll %>% 
  mutate('Post-publication critique type' = "All types") %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianLength, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

``` {r}
# Summarise length Statistics for each PPC type
randomLengthType <- dj_random %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_length)) %>%
 mutate(quantLength = case_when(
    ppc_length == "NOT STATED" | ppc_length == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_length) # create a column that contains only quantitative limits
  )) %>%
 group_by(ppc_name) %>%
 summarise(
    anyLimit = n() - sum(ppc_length == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_length == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianLength = median(quantLength, na.rm = TRUE),
    Q1 = round(quantile(quantLength, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantLength, probs = 0.75, na.rm = TRUE)),
    IQR = Q3 - Q1 
 ) %>%
  ungroup()

# Put results into desired table format
randomLengthType_1 <- randomLengthType %>% 
  mutate('Post-publication critique type' = ppc_name) %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianLength, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Combine all time limits into single table
randomLength_combo <- bind_rows(
  randomLengthType_1,
  randomLengthAll_1
)
```

Check time-to-submit limits placed on PPC options in prominent journals
```{r}
# Summarise time-to-submit statistics for All Types
randomTimeAll <- dj_random %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_time)) %>%
 mutate(quantTime = case_when(
    ppc_time == "NOT STATED" | ppc_time == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_time) # create a column that contains only quantitative limits
  )) %>%
 summarise(
    anyLimit = n() - sum(ppc_time == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_time == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianTime = median(quantTime, na.rm = TRUE),
    Q1 = round(quantile(quantTime, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantTime, probs = 0.75, na.rm = TRUE)),
    IQR = Q3 - Q1 
 ) 

# Put results into desired table format
randomTimeAll_1 <- randomTimeAll %>% 
  mutate('Post-publication critique type' = "All Types") %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianTime, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

``` {r}
# Summarise time-to-submit Statistics for each PPC type
randomTimeType <- dj_random %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_time)) %>%
 mutate(quantTime = case_when(
    ppc_time == "NOT STATED" | ppc_time == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_time) # create a column that contains only quantitative limits
  )) %>%
  group_by(ppc_name) %>%
 summarise(
    anyLimit = n() - sum(ppc_time == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_time == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianTime = median(quantTime, na.rm = TRUE),
    Q1 = round(quantile(quantTime, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantTime, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1)
 ) %>%
  ungroup()

# Put results into desired table format
randomTimeType_1 <- randomTimeType %>% 
  mutate('Post-publication critique type' = ppc_name) %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianTime, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Combine all time limits into single table
randomTime_combo <- bind_rows(
  randomTimeType_1,
  randomTimeAll_1
)
```

Check reference limits placed on PPC options in prominent journals
```{r}
# Summarise reference statistics for All Types
randomRefAll <- dj_random %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_ref)) %>%
 mutate(quantRef = case_when(
    ppc_ref == "NOT STATED" | ppc_ref == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_ref) # create a column that contains only quantitative limits
  )) %>%
 summarise(
    anyLimit = n() - sum(ppc_ref == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_ref == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianRef = median(quantRef, na.rm = TRUE),
    Q1 = round(quantile(quantRef, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantRef, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1)
 )

# Put results into desired table format
randomRefAll_1 <- randomRefAll %>% 
  mutate('Post-publication critique type' = "All types") %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianRef, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Summarise reference statistics by type
randomRefType <- dj_random %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_ref)) %>%
 mutate(quantRef = case_when(
    ppc_ref == "NOT STATED" | ppc_ref == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_ref) # create a column that contains only quantitative limits
  )) %>%
  group_by(ppc_name) %>%
 summarise(
    anyLimit = n() - sum(ppc_ref == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_ref == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianRef = median(quantRef, na.rm = TRUE),
    Q1 = round(quantile(quantRef, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantRef, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1)
 ) %>%
  ungroup()

# Put results into desired table format
randomRefType_1 <- randomRefType %>% 
  mutate('Post-publication critique type' = ppc_name) %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianRef, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Combine all peer review into single table
randomRef_combo <- bind_rows(
  randomRefType_1,
  randomRefAll_1
)
```

Check how many PPC options are sent for external peer review in prominent journals
```{r}
# Peer review statistics for All Types
randomReviewAll <- dj_random %>%
  select(c(journal_name, ppc_name, ppc_review)) %>%
  filter(!is.na(ppc_name)) %>%
  summarise(anyReview = n() - sum(ppc_review == "NOT STATED"),
            yesReview = anyReview - sum(ppc_review == "NO"),
            yesPercent = round((yesReview / n()) * 100)   # Percentage reviewed from All Types 
  )

# Put results into desired table format
randomReviewAll_1 <- randomReviewAll %>%
  mutate('Post-publication critique type' = "All types") %>%
  mutate('YES n (%)' = paste(yesReview, " (", yesPercent, ")", sep = "")) %>%
  select('Post-publication critique type', 'YES n (%)')
```

```{r}
# Peer review statistics by types
randomReviewType <- dj_random %>%
  select(c(journal_name, ppc_name, ppc_review)) %>%
  filter(!is.na(ppc_name)) %>%
  group_by(ppc_name) %>%
  summarise(anyReview = n() - sum(ppc_review == "NOT STATED"),
            yesReview = anyReview - sum(ppc_review == "NO"),
            yesPercent = round((yesReview / n()) * 100)
  ) %>%
  ungroup()

# Put results into desired table format
randomReviewType_1 <- randomReviewType %>%
  mutate('Post-publication critique type' = ppc_name) %>%
  mutate('YES n (%)' = paste(yesReview, " (", yesPercent, ")", sep = "")) %>%
  select('Post-publication critique type', 'YES n (%)')
```

```{r}
# Combine all peer review into single table
randomReview_combo <- bind_rows(
  randomReviewType_1,
  randomReviewAll_1
)
```

**Table 1.** Post-publication critique types identified in randomly selected psychology journals and their length, time-to-submit, and reference limits. 

``` {r}
# Give each table a separate header for results
randomLengthTable <- randomLength_combo %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "any n (%)", 
                              "quantitative n (%)", 
                              "median (IQR)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Length limits" = 3))

randomTimeTable <- randomTime_combo %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "any n (%)", 
                              "quantitative n (%)", 
                              "median (IQR)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Time limits" = 3))

randomRefTable <- randomRef_combo %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "any n (%)", 
                              "quantitative n (%)", 
                              "median (IQR)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Reference limits" = 3))

randomReviewTable <- randomReview_combo %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "YES n (%)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Peer review" = 1))
```

```{r}
# Combine the random sample limitations data frames
combined_df <- bind_cols(
  randomLength_combo %>% select(-`Post-publication critique type`),
  randomTime_combo %>% select(-`Post-publication critique type`),
  randomRef_combo %>% select(-`Post-publication critique type`),
  randomReview_combo %>% select(-`Post-publication critique type`)
)

# Add the 'Post-publication critique type' column back to the combined data frame
combined_df <- bind_cols(randomLength_combo %>% select(`Post-publication critique type`), combined_df)

# Create the table with kableExtra
randomLimits_Table <- combined_df %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "any n (%)", "quantitative n (%)", "median (IQR)",
                              "any n (%)", "quantitative n (%)", "median (IQR)",
                              "any n (%)", "quantitative n (%)", "median (IQR)",
                              "YES n (%)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Length limits" = 3, "Time limits" = 3, "Reference limits" = 3, "Peer review" = 1))

randomLimits_Table

save_kable(randomLimits_Table, here("analysis/randomLimits_Table.png"))
```

## Calculations for Table 2: PPC limits in prominent journals

Check length limits placed on PPC options in prominent journals
```{r}
# Summarise length statistics for All Types
prominentLengthAll <- dj_prominent %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_length)) %>%
 mutate(quantLength = case_when(
    ppc_length == "NOT STATED" | ppc_length == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_length) # create a column that contains only quantitative limits
  )) %>%
 summarise(
    anyLimit = n() - sum(ppc_length == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_length == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianLength = median(quantLength, na.rm = TRUE),
    Q1 = round(quantile(quantLength, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantLength, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1)
 ) 

# Put results into desired table format
prominentLengthAll_1 <- prominentLengthAll %>% 
  mutate('Post-publication critique type' = "All types") %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianLength, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

``` {r}
# Summarise length Statistics for each PPC type
prominentLengthType <- dj_prominent %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_length)) %>%
 mutate(quantLength = case_when(
    ppc_length == "NOT STATED" | ppc_length == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_length) # create a column that contains only quantitative limits
  )) %>%
 group_by(ppc_name) %>%
 summarise(
    anyLimit = n() - sum(ppc_length == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_length == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianLength = median(quantLength, na.rm = TRUE),
    Q1 = round(quantile(quantLength, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantLength, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1)
 ) %>%
  ungroup()

# Put results into desired table format
prominentLengthType_1 <- prominentLengthType %>% 
  mutate('Post-publication critique type' = ppc_name) %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianLength, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Combine all peer review into single table
prominentLength_combo <- bind_rows(
  prominentLengthType_1,
  prominentLengthAll_1
)
```

Check time-to-submit limits placed on PPC options in prominent journals
```{r}
# Summarise time-to-submit statistics for All Types
prominentTimeAll <- dj_prominent %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_time)) %>%
 mutate(quantTime = case_when(
    ppc_time == "NOT STATED" | ppc_time == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_time) # create a column that contains only quantitative limits
  )) %>%
 summarise(
    anyLimit = n() - sum(ppc_time == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_time == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianTime = round(median(quantTime, na.rm = TRUE)),
    Q1 = round(quantile(quantTime, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantTime, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1) 
 ) 

# Put results into desired table format
prominentTimeAll_1 <- prominentTimeAll %>%
  mutate('Post-publication critique type' = "All types") %>%
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>%
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>%
  mutate('median (IQR)' = paste(medianTime, " (", Q1, " - ", Q3, ")", sep = "")) %>%
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

``` {r}
# Summarise time-to-submit Statistics for each PPC type
prominentTimeType <- dj_prominent %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_time)) %>%
 mutate(quantTime = case_when(
    ppc_time == "NOT STATED" | ppc_time == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_time) # create a column that contains only quantitative limits
  )) %>%
  group_by(ppc_name) %>%
 summarise(
    anyLimit = n() - sum(ppc_time == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_time == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianTime = round(median(quantTime, na.rm = TRUE)),
    Q1 = round(quantile(quantTime, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantTime, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1)
 ) %>%
  ungroup()

# Put results into desired table format
prominentTimeType_1 <- prominentTimeType %>%
  mutate('Post-publication critique type' = ppc_name) %>%
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>%
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>%
  mutate('median (IQR)' = paste(medianTime, " (", Q1, " - ", Q3, ")", sep = "")) %>%
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Combine all peer review into single table
prominentTime_combo <- bind_rows(
  prominentTimeType_1,
  prominentTimeAll_1
)
```

Check reference limits placed on PPC options in prominent journals
```{r}
# Summarise reference statistics for All Types
prominentRefAll <- dj_prominent %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_ref)) %>%
 mutate(quantRef = case_when(
    ppc_ref == "NOT STATED" | ppc_ref == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_ref) # create a column that contains only quantitative limits
  )) %>%
 summarise(
    anyLimit = n() - sum(ppc_ref == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_ref == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianRef = median(quantRef, na.rm = TRUE),
    Q1 = round(quantile(quantRef, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantRef, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1)
 ) 

# Put results into desired table format
prominentRefAll_1 <- prominentRefAll %>%
  mutate('Post-publication critique type' = "All types") %>%
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>%
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>%
  mutate('median (IQR)' = paste(medianRef, " (", Q1, " - ", Q3, ")", sep = "")) %>%
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Summarise reference statistics by type
prominentRefType <- dj_prominent %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_ref)) %>%
 mutate(quantRef = case_when(
    ppc_ref == "NOT STATED" | ppc_ref == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_ref) # create a column that contains only quantitative limits
  )) %>%
  group_by(ppc_name) %>%
 summarise(
    anyLimit = n() - sum(ppc_ref == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_ref == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianRef = median(quantRef, na.rm = TRUE),
    Q1 = round(quantile(quantRef, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantRef, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1)
 ) %>%
  ungroup()

# Put results into desired table format
prominentRefType_1 <- prominentRefType %>%
  mutate('Post-publication critique type' = ppc_name) %>%
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>%
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>%
  mutate('median (IQR)' = paste(medianRef, " (", Q1, " - ", Q3, ")", sep = "")) %>%
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Combine all peer review into single table
prominentRef_combo <- bind_rows(
  prominentRefType_1,
  prominentRefAll_1
)
```

Check how many PPC options are sent for external peer review in prominent journals
```{r}
# Peer review statistics for All Types
prominentReviewAll <- dj_prominent %>%
  select(c(journal_name, ppc_name, ppc_review)) %>%
  filter(!is.na(ppc_name)) %>%
  summarise(anyReview = n() - sum(ppc_review == "NOT STATED"),
            yesReview = anyReview - sum(ppc_review == "NO"),
            yesPercent = round((yesReview / n()) * 100)   # Percentage reviewed from All Types 
  )

# Put results into desired table format
prominentReviewAll_1 <- prominentReviewAll %>%
  mutate('Post-publication critique type' = "All types") %>%
  mutate('YES n (%)' = paste(yesReview, " (", yesPercent, ")", sep = "")) %>%
  select('Post-publication critique type', 'YES n (%)')
```

```{r}
# Peer review statistics by types
prominentReviewType <- dj_prominent %>%
  select(c(journal_name, ppc_name, ppc_review)) %>%
  filter(!is.na(ppc_name)) %>%
  group_by(ppc_name) %>%
  summarise(anyReview = n() - sum(ppc_review == "NOT STATED"),
            yesReview = anyReview - sum(ppc_review == "NO"),
            yesPercent = round((yesReview / n()) * 100)
  ) %>%
  ungroup()

# Put results into desired table format
prominentReviewType_1 <- prominentReviewType %>%
  mutate('Post-publication critique type' = ppc_name) %>%
  mutate('YES n (%)' = paste(yesReview, " (", yesPercent, ")", sep = "")) %>%
  select('Post-publication critique type', 'YES n (%)')
```

```{r}
# Combine all peer review into single table
prominentReview_combo <- bind_rows(
  prominentReviewType_1,
  prominentReviewAll_1
)
```

**Table 2.** Post-publication critique types identified in prominent psychology journals and their length, time-to-submit, and reference limits. 

``` {r}
# Give each table a separate header for results
prominentLengthTable <- prominentLength_combo %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "any n (%)", 
                              "quantitative n (%)", 
                              "median (IQR)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Length limits" = 3))

prominentTimeTable <- prominentTime_combo %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "any n (%)", 
                              "quantitative n (%)", 
                              "median (IQR)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Time limits" = 3))

prominentRefTable <- prominentRef_combo %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "any n (%)", 
                              "quantitative n (%)", 
                              "median (IQR)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Reference limits" = 3))

prominentReviewTable <- prominentReview_combo %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "YES n (%)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Peer review" = 1))

```

```{r}
# Combine the prominent limitations data frames
combined_df <- bind_cols(
  prominentLength_combo %>% select(-`Post-publication critique type`),
  prominentTime_combo %>% select(-`Post-publication critique type`),
  prominentRef_combo %>% select(-`Post-publication critique type`),
  prominentReview_combo %>% select(-`Post-publication critique type`)
)

# Add the 'Post-publication critique type' column back to the combined data frame
combined_df <- bind_cols(prominentLength_combo %>% select(`Post-publication critique type`), combined_df)

# Create the table with kableExtra
prominentLimits_Table <- combined_df %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "any n (%)", "quantitative n (%)", "median (IQR)",
                              "any n (%)", "quantitative n (%)", "median (IQR)",
                              "any n (%)", "quantitative n (%)", "median (IQR)",
                              "YES n (%)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Length limits" = 3, "Time limits" = 3, "Reference limits" = 3, "Peer review" = 1))

prominentLimits_Table

save_kable(prominentLimits_Table, here("analysis/prominentLimits_Table.png"))
```

# STUDY 2: PREVALENCE 

## Prevalence in randomly selected journals

Look for linked PPC in articles in random sample
```{r}
d_articles %>%
  filter(sample_id == "random",
         ppc_linked == TRUE) %>%
  summarise(n = n())
```

Calculate CIs for linked PPC in articles in random sample
```{r}
# Specify sample size for articles (same for both samples)
sample_size_a <- 101

# Linked PPCs
random_linked <- d_articles %>% # counts number of linked PPC events
  filter(sample_id == "random",
         ppc_linked == TRUE) %>%
  count()

ci_Rlinked <- binom.confint(random_linked$n, sample_size_a, method = "wilson", conf.level = confidence_level)

# Convert the lower and upper limits to percentages and round them to one decimal place
ci_randLinked_LL <- round(ci_Rlinked$lower*100, 1)
ci_randLinked_UL <- round(ci_Rlinked$upper*100, 1)

ci_randLinked_LL
ci_randLinked_UL
```

Look for instances of PPC in articles in random sample
```{r}
d_articles %>%
  filter(sample_id == "random",
         exclude_reason == "IS ITSELF PPC") %>%
  summarise(n = n())
```

Calculate CIs for Instance PPC in random sample
```{r}
# Instance PPCs
random_instance <- d_articles %>% # counts number of linked PPC events
  filter(sample_id == "random",
    exclude_reason == "IS ITSELF PPC") %>%
  count()

ci_Rinstance <- binom.confint(random_instance$n, sample_size_a, method = "wilson", conf.level = confidence_level)

# Convert the lower and upper limits to percentages and round them to one decimal place
ci_randInstance_LL <- round(ci_Rinstance$lower*100, 1)
ci_randIinstance_UL <- round(ci_Rinstance$upper*100, 1)

ci_randInstance_LL
ci_randIinstance_UL
```

## Prevalence in prominent journals

Look for links to PPC in articles published in prominent journals
```{r}
d_articles %>%
  filter(sample_id == "prominent",
         ppc_linked == TRUE) %>%
  summarise(n = n())
```

Calculate CIs for Linked PPC 
```{r}
# Linked PPCs
prominent_linked <- d_articles %>% # counts number of linked PPC events
  filter(sample_id == "prominent",
         ppc_linked == TRUE) %>%
  count()

ci_linked <- binom.confint(prominent_linked$n, sample_size_a, method = "wilson", conf.level = confidence_level)

# Convert the lower and upper limits to percentages and round them to one decimal place
ci_promLinked_LL <- round(ci_linked$lower*100, 1)
ci_promLinked_UL <- round(ci_linked$upper*100, 1)

ci_promLinked_LL
ci_promLinked_UL
```

Look for instances of PPC in articles published in prominent journals
```{r}
d_articles %>%
  filter(sample_id == "prominent",
         exclude_reason == "IS ITSELF PPC") %>%
  summarise(n = n())
```

Calculate CIs for Instance PPC in prominent journals
```{r}
# Instance PPCs
prominent_instance <- d_articles %>% # counts number of linked PPC events
  filter(sample_id == "prominent",
    exclude_reason == "IS ITSELF PPC") %>%
  count()

ci_instance <- binom.confint(prominent_instance$n, sample_size_a, method = "wilson", conf.level = confidence_level)

# Convert the lower and upper limits to percentages and round them to one decimal place
ci_promInstance_LL <- round(ci_instance$lower*100, 1)
ci_promIinstance_UL <- round(ci_instance$upper*100, 1)

ci_promInstance_LL
ci_promIinstance_UL
```

\end

## Journal Policy Figures for Conference Presentation

```{r}
dj_prominent %>% 
  filter(ppc_type == "A") %>% 
  mutate(has_ppc = case_when(
    has_ppc == "NO EXPLICIT" ~ "NO",
    has_ppc == "NO IMPLICIT" ~ "NO",
    TRUE ~ has_ppc
  )) %>% 
  ggplot(aes(x = has_ppc, fill = has_ppc)) +
  geom_bar(alpha = 0.7,
           colour = "black",
           width = 0.9,
           show.legend = F
           ) +
  theme(aspect.ratio = 2/1) +
  labs(title = "Prominent Journals", x = "", y ="Number of Journals (N = 100)") +
  scale_fill_brewer(palette = "Paired") +
  scale_y_continuous(limits = c(0, 100)) +
  theme(
    axis.text.x = element_text(size = 14),  
    axis.text.y = element_text(size = 14)
  )

ggsave("prom_plot.png", plot = last_plot())
```

```{r}
# Calculate Wilson confidence intervals
dj_random_sum <- dj_random %>% 
  filter(ppc_type == "A") %>% 
  mutate(has_ppc = case_when(
    has_ppc == "NO EXPLICIT" ~ "NO",
    has_ppc == "NO IMPLICIT" ~ "NO",
    TRUE ~ has_ppc)
  ) %>% 
  group_by(has_ppc) %>% 
   summarise(count = n()) %>% 
  mutate(
    LL = case_when(
      has_ppc == "YES" ~ 16,
      has_ppc == "NO" ~ 68
    ),
    UL = case_when(
      has_ppc == "YES" ~ 32,
      has_ppc == "NO" ~ 84
    )
  )

# Plot with error bars
dj_random_sum %>% 
  ggplot(aes(x = has_ppc, y = count, fill = has_ppc)) +
  geom_bar(stat = "identity", 
           alpha = 0.7, 
           colour = "black",
           width = 0.9,
           show.legend = F
           ) +
   theme(aspect.ratio = 2/1) +
  geom_errorbar(aes(ymin = LL, ymax = UL), width = 0.2) +
  labs(title = "Randomly Selected Journals", x = "", y = "Number of Journals  (N = 100)") +
  scale_fill_brewer(palette = "Greens") +
  scale_y_continuous(limits = c(0, 100)) +
  theme(
    axis.text.x = element_text(size = 14),  
    axis.text.y = element_text(size = 14)
  ) 

ggsave("random_plot.png", plot = last_plot())
```

